Multilevel computation of glacier geometry \\ from Stokes dynamics

### 2022-10-15 paper/msg.tex
correct a published ref

Patch-type smoothers \cite{Farrelletal2019} have to our knowledge not been used for VI problems before, but they would sweep through the nodes solving local VIs of small dimension $\ell>1$, and again there would be serial and parallel versions.  However, we first consider the opposite extreme from a pointwise smoother, namely a global smoother in which all the degrees of freedom are coupled together into an algebraic system.

>>>>

Patch-type smoothers \cite{Farrelletal2021} have to our knowledge not been used for VI problems before, but they would sweep through the nodes solving local VIs of small dimension $\ell>1$, and again there would be serial and parallel versions.  However, we first consider the opposite extreme from a pointwise smoother, namely a global smoother in which all the degrees of freedom are coupled together into an algebraic system.
